Depth and thickness of tectonic tremor in the northeastern Olympic Peninsula

### 2021-12-03 paper/agujournaltemplate.tex
Add plain language

\begin{keypoints}
\item We use seismic data from small-aperture arrays in the Olympic Peninsula, Washington and tremor epicenters determined previously by a multibeam backprojection method. 
\item We compute the depth of the tremor source from estimates of S minus P times determined from stacking horizontal-to-vertical cross-correlations of seismic data.
\item Tremor is located close to the plate boundary in a region no more than 2-3 kilometers thick.
\end{keypoints}

@@

\begin{abstract}
Tectonic tremor has been explained as a swarm of low-frequency earthquakes, which are located on a narrow fault at the plate boundary. However, due to the lack of clear impulsive phases in the tremor signal, it is difficult to determine the depth of the tremor source and the distance of the source to the plate interface with great precision. The thickness of the tremor region is also not well constrained. The tremor may be located on a narrow fault as the low-frequency earthquakes appear to be, or distributed over a few kilometers wide low shear-wave velocity layer in the upper oceanic crust, which is thought to be a region with high pore-fluid pressure. Lag times of peaks in the cross-correlation of the horizontal and vertical components of tremor seismograms, recorded by small-aperture arrays in the Olympic Peninsula, Washington, are interpreted to be S minus P times.  Tremor depths are estimated from these S minus P times using epicenters from a previous study using a multibeam backprojection method. The tremor is located close to the plate boundary in a region no more than 2-3 kilometers thick and is very close to the depths of low-frequency earthquakes. The tremor is distributed over a wider depth range than the low-frequency earthquakes. However, due to the uncertainty on the depth, it is difficult to conclude whether the source of the tremor is located at the top of the subducting oceanic crust, in the lower continental crust just above the plate boundary, or in a narrow zone at the plate boundary.
\end{abstract}

%\section*{Plain Language Summary}
%[ enter your Plain Language Summary here or delete this section]

>>>>

\begin{keypoints}
\item We use seismic data from small-aperture arrays in the Olympic Peninsula, and tremor epicenters determined by a previous study. 
\item We compute the depth of the tremor from S minus P times determined from stacking horizontal-to-vertical cross-correlations of seismic data.
\item Tremor is located close to the plate boundary in a region no more than 2-3 kilometers thick.
\end{keypoints}

@@

\begin{abstract}
Tectonic tremor has been explained as a swarm of low-frequency earthquakes, which are located on a narrow fault at the plate boundary. However, due to the lack of clear impulsive phases in the tremor signal, it is difficult to determine the depth of the tremor source with great precision. The thickness of the tremor region is also not well constrained. The tremor may be located on a narrow fault as the low-frequency earthquakes appear to be, or distributed over a few kilometers wide low shear-wave velocity layer in the upper oceanic crust, which is thought to be a region with high pore-fluid pressure. Lag times of peaks in the cross-correlation of the horizontal and vertical components of tremor seismograms, recorded by small-aperture arrays in the Olympic Peninsula, Washington, are interpreted to be S minus P times.  Tremor depths are estimated from these S minus P times using epicenters from a previous study using a multibeam backprojection method. The tremor is located close to the plate boundary in a region no more than 2-3 kilometers thick and is very close to the depths of low-frequency earthquakes. The tremor is distributed over a wider depth range than the low-frequency earthquakes. However, due to the uncertainty on the depth, it is difficult to conclude whether the source of the tremor is located at the top of the subducting oceanic crust, in the lower continental crust just above the plate boundary, or in a narrow zone at the plate boundary.
\end{abstract}

\section*{Plain Language Summary}
Tectonic tremor is a long, low amplitude seismic signal, with emergent onsets, and an absence of clear impulsive phases. It has been explained as a swarm of low-frequency earthquakes, which are located on a narrow fault at the plate boundary. It is therefore assumed that the source of the tectonic tremor is located close to the plate boundary. However, due to the lack of clear impulsive phases in the tremor signal, it is difficult to determine the depth of the tremor source and the distance of the source to the plate interface with great precision. The thickness of the tremor region is not well constrained either. The tremor may be located on a narrow fault like the low-frequency earthquakes, or distributed through a few kilometers wide low shear-wave velocity layer in the upper oceanic crust, which is thought to be a region with high pore-fluid pressure. In this paper, we show that the tremor is located close to the plate boundary in a region no more than 2-3 kilometers thick and is very close to the depths of low-frequency earthquakes. Knowing the depth of the tremor source will help understand the mechanism that produces the tremor.
